% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}

\begin{experiences}
    \experience
        {June 2020}
        {Software Engineer}
        {\link{https://shahry.app/en/}{Shahry}}
        {Present}
        {
            \begin{itemize}
                \item Initiated in-store payments by developing external Restful APIs and
                integrating with three external merchants, thus increasing sales.
                \item Improved fault isolation by refactoring parts of the monolith service into smaller independent services, while retaining communication with the monolith service using RabbitMQ.
                \item Reduced dashboard API development time, by switching to GraphQL, easier to develop nested relation API faster.
                \item Presented and advocated for a system-wide \link{https://github.com/HackSoftware/Django-Styleguide}{style-guide}, enhancing code readability and consistency.
                \item Enhanced App-to-server communication security by migrating to Knox tokens without logout incidents.
                \item Headed external API integrations including but not limited to Bank Reports, Social Insurance API and Background Check API.
            \end{itemize}
        }
        {
            Python,
            Django,
            RESTful,
            DRF,
            GraphQL,
            Graphene,
            Docker,
            Docker Compose,
            Docker Swarm,
            Jenkins CI/CD,
            PostgreSQL,
            Jira,
            Traefik,
            Sentry,
            Portainer,
            Scout APM,
            RabbitMQ,
            Redis
        }
    \emptySeparator

    \experience
        {June 2019}
        {Software Engineer}
        {\link{https://www.linkedin.com/company/infme.com/}{Informatica Middle East}}
        {June 2020}
        {
            \begin{itemize}
                \item Established the first digital internal HR platfrom, reducing  overhead paperwork and accommodating the COVID-19 shutdown.
                \item Streamlined bank E-statement generation and send flow by reducing by removing redundancies in flow, thus reducing file-size by 400\%.
                \item Facilitated dashboard search by developing a cross-linguistic search on names and addresses in an Arabic-English database.
            \end{itemize}
        }
        {
            Python,
            Odoo - Python,
            NLTK - Python,
            Java,
            iText - Java,
            Informatica Powercenter,
            Birt reports
        }
\end{experiences}
